The Impact of Past Behavior Normality on Regret: A Replication Study

### 2024-02-15 outputs/paper/Paper_2.qmd
update

From the article, we can see that among 277 people, 81% believe that a person named White who was involved in a similar accident while driving on a route he only took for a change of scenery would feel greater regret and worse luck. Therefore, the factor of luck often has a direct relationship with the level of regret. When someone encounters a random event, the worse their luck, the stronger their feeling of regret. For example, Mr. Adams had an accident while driving home on his usual route after work. Mr. White had a similar accident while he was driving on a route he only took when he wanted a change of scenery. In such cases, for accidents that happen under normal circumstances, people might think that it was something bound to happen, believing that no matter what, if they were on that road, they would have faced the same situation, and thus, they wouldn't particularly feel unlucky or have much regret (Kutscher & Feldman 2019). However, people tend to attribute accidents that happen under unusual circumstances to bad luck. Mr. White's temporary choice led to a bad outcome. Since there was no way to weigh the probabilities of different choices at the moment of decision, people are more likely to attribute the event to bad luck, resulting in a stronger sense of regret.

The way people understand luck in relation to regret is detailed and subtle. Essentially, luck is about the element of chance in what happens after we make decisions or take actions. When people think that what happens is down to luck, their feelings of regret can change depending on how much control they think they had over the situation. If someone believes a bad outcome was just unlucky, they might not feel as much regret because they see it as something they couldn't avoid. On the other hand, if they see the outcome as the result of their own choices, the regret can be stronger because they think they could have chosen differently to prevent the bad result (Kutscher & Feldman 2019). This shows that how much regret people feel isn't just about what happens, but also how they interpret these happenings in terms of luck and their own actions.

@@

The interplay between counterfactual thinking and the consequent feelings of regret significantly influences individuals' expectations for compensation, a dynamic vividly illustrated through the experiences of White and Smith. Counterfactual thinking, the cognitive process of envisioning alternative scenarios that did not occur, can intensify feelings of regret, especially when these imagined outcomes are perceived as more favorable than the actual events. For White, who frequented a familiar store and experienced a robbery resulting in severe injury, the compensation expectations are densely clustered around $500,000, suggesting that the routine nature of his visit might have led to less intense counterfactual thinking and subsequently, a more contained range of expected compensation. In contrast, Smith, who ventured into an unfamiliar store under unusual circumstances and encountered the same fate, experiences stronger regret, fueled by more potent counterfactual thoughts such as "If only I had avoided making that unusual choice." This heightened level of regret is reflected in the more dispersed compensation expectations, with most believing that the figure should lie between ¥500,000 and ¥1,000,000. This scenario underlines how the depth and focus of counterfactual thinking can dramatically shape an individual's perception of their loss and their valuation of necessary compensation. It showcases the complex relationship between cognitive processes and emotional responses, demonstrating that individuals' compensation expectations are not only a reflection of their physical losses but also an attempt to mitigate the emotional distress caused by their reflections on what could have been, thus highlighting the profound impact of counterfactual thinking on human behavior and expectations in the aftermath of traumatic events (Kutscher & Feldman 2019).

# Conclusion

This article delves into how people perceive and process regret across various situations, from offering help that leads to negative outcomes, to the role luck plays in our feelings of regret, and finally, how we value compensation after unfortunate events. It highlights how our thoughts about "what could have been," our views on chance, and our expectations for making amends are deeply intertwined with our emotional reactions. The study reveals the complexity of our emotional world and how our minds influence our feelings and choices after difficult situations. By understanding these relationships, we gain insight into the complex nature of human emotions and the significant impact our cognitive and emotional responses have on how we navigate and make sense of challenges in our lives.

>>>>

From the article, we can see that among 277 people, 81% believe that a person named White who was involved in a similar accident while driving on a route he only took for a change of scenery would feel greater regret and worse luck. Therefore, the factor of luck often has a direct relationship with the level of regret. When someone encounters a random event, the worse their luck, the stronger their feeling of regret. For example, Mr. Adams had an accident while driving home on his usual route after work. Mr. White had a similar accident while he was driving on a route he only took when he wanted a change of scenery. In such cases, for accidents that happen under normal circumstances, people might think that it was something bound to happen, believing that no matter what, if they were on that road, they would have faced the same situation, and thus, they wouldn't particularly feel unlucky or have much regret (Kutscher & Feldman, 2019). However, people tend to attribute accidents that happen under unusual circumstances to bad luck. Mr. White's temporary choice led to a bad outcome. Since there was no way to weigh the probabilities of different choices at the moment of decision, people are more likely to attribute the event to bad luck, resulting in a stronger sense of regret.

The way people understand luck in relation to regret is detailed and subtle. Essentially, luck is about the element of chance in what happens after we make decisions or take actions. When people think that what happens is down to luck, their feelings of regret can change depending on how much control they think they had over the situation. If someone believes a bad outcome was just unlucky, they might not feel as much regret because they see it as something they couldn't avoid. On the other hand, if they see the outcome as the result of their own choices, the regret can be stronger because they think they could have chosen differently to prevent the bad result (Kutscher & Feldman, 2019). This shows that how much regret people feel isn't just about what happens, but also how they interpret these happenings in terms of luck and their own actions.

@@

The interplay between counterfactual thinking and the consequent feelings of regret significantly influences individuals' expectations for compensation, a dynamic vividly illustrated through the experiences of White and Smith. Counterfactual thinking, the cognitive process of envisioning alternative scenarios that did not occur, can intensify feelings of regret, especially when these imagined outcomes are perceived as more favorable than the actual events. For White, who frequented a familiar store and experienced a robbery resulting in severe injury, the compensation expectations are densely clustered around $500,000, suggesting that the routine nature of his visit might have led to less intense counterfactual thinking and subsequently, a more contained range of expected compensation. In contrast, Smith, who ventured into an unfamiliar store under unusual circumstances and encountered the same fate, experiences stronger regret, fueled by more potent counterfactual thoughts such as "If only I had avoided making that unusual choice." This heightened level of regret is reflected in the more dispersed compensation expectations, with most believing that the figure should lie between ¥500,000 and ¥1,000,000. This scenario underlines how the depth and focus of counterfactual thinking can dramatically shape an individual's perception of their loss and their valuation of necessary compensation. It showcases the complex relationship between cognitive processes and emotional responses, demonstrating that individuals' compensation expectations are not only a reflection of their physical losses but also an attempt to mitigate the emotional distress caused by their reflections on what could have been, thus highlighting the profound impact of counterfactual thinking on human behavior and expectations in the aftermath of traumatic events (Kutscher & Feldman, 2019).

# Conclusion
This article delves into how people perceive and process regret across various situations, from offering help that leads to negative outcomes, to the role luck plays in our feelings of regret, and finally, how we value compensation after unfortunate events. It highlights how our thoughts about "what could have been," our views on chance, and our expectations for making amends are deeply intertwined with our emotional reactions. The study reveals the complexity of our emotional world and how our minds influence our feelings and choices after difficult situations. By understanding these relationships, we gain insight into the complex nature of human emotions and the significant impact our cognitive and emotional responses have on how we navigate and make sense of challenges in our lives.
